### 2025-02-24 paper/sections/appendix.qmd
buff

# Notation {.appendix}

- $y^+$: The target class and also the index of the target class.
- $y^-$: The non-target class and also the index of non-the target class.
- $\mathbf{y}^+$: The one-hot encoded output vector for the target class. 
- $\theta$: Model parameters (unspecified).
- $\Theta$: Matrix of parameters.

@@

\@Cynthia, \@Arie, I'm including some preliminary results here but will rerun experiments in the coming days. You'll notice some odd outlier results (huge values) for the initial grid search (@sec-app-initial). My belief is that this is once again due to *ECCo* overshooting for some hyperparameter choices, that we have discussed before. A simple solution to this story is to actually impose domain constraints. Let's see what the final results show us (I also still plan to make slight changes to the implementation), but in any case I think it might even be worth to report results for the initial grid search in the final appendix (they do include good results for CT for certain hyperparameter ranges and highlight limitations inherited from energy-based modelling).

@@

\@Cynthia, \@Arie, @fig-mnist shows much more plausible (faithful) counterfactuals for a model with CT than the model with conventional training (@fig-mnist-vanilla). In fact, this is not even using *ECCo+* and still showing better results than the best results we achieved in our AAAI paper for JEM ensembles.

@@

# Compute {.appendix}

<!-- [@DHPC2022] -->

We performed our experiments on a high-performance cluster. Details about the cluster will be disclosed upon publication to avoid revealing information that might interfere with the double-blind review process. Since our experiments have largely involved highly parallel tasks and small models, we have made extensive use of multi-processing.

>>>>

{{< include /paper/sections/other/notation.qmd >}}

@@

I'm including some preliminary results here but will rerun experiments in the coming days. You'll notice some odd outlier results (huge values) for the initial grid search (@sec-app-initial). My belief is that this is once again due to *ECCo* overshooting for some hyperparameter choices, that we have discussed before. A simple solution to this story is to actually impose domain constraints. Let's see what the final results show us (I also still plan to make slight changes to the implementation), but in any case I think it might even be worth to report results for the initial grid search in the final appendix (they do include good results for CT for certain hyperparameter ranges and highlight limitations inherited from energy-based modelling).

@@

@fig-mnist shows much more plausible (faithful) counterfactuals for a model with CT than the model with conventional training (@fig-mnist-vanilla). In fact, this is not even using *ECCo+* and still showing better results than the best results we achieved in our AAAI paper for JEM ensembles.

@@

{{< include /paper/sections/other/compute.qmd >}}
